Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-08-23 tex/main/manuscript.tex
修改讨论第二节第一段，以及做新图

\subsection*{Development Traps}
% 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
Since each basin at different transition phase, 
they are facing different development traps regarding water utilization, 
leading an unsustainable trajectory. 
Like social-ecological systems and other complex systems, 
coupled human-water system disintegrate may occurred under the gradual pressure of rising resources, 
or collapse emerged because of structural mismatches.
A number of studies have identified transformation as an important way out of unsustainable trajectory, 
and different types of transformation are required according to dominating phases and traps of systems.
Thus, it is crucial to distinguish major development traps 
based on the transition framework of water utilization regimes.

>>>>

\subsection*{Development Traps}
% 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
At different transition phases, basins may face to various development traps in water utilization, leading an unsustainable trajectory (Figure~\ref{fig:traps}). Like social-ecological systems and other complex systems, coupled human-water system disintegrate may occurred under the gradual pressure of rising resources, or collapse emerged because of structural mismatches. A number of studies have identified transformation as an important way out of unsustainable trajectory, and different types of transformation are required according to dominating phases and traps of systems. Thus, it is crucial to distinguish major development traps based on the transition framework of water utilization regimes.

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/traps.jpg}
	\caption{
		\textbf{Transition phases of water resources utilization regime and development traps.}
		Green arrows indicate the trajectory without falling into any development trap, IWRU roughly follows a non-linear upward trend at the same time. However, overexploitation of water resources will leave the system in a local resource trap, without moving to regional coordinated cycle. And even if one enters a regional cycle, it can still fall into a structural trap when water utilization fails to adapt to the complex changes within human-water systems.
	}
	\label{fig:traps}
\end{figure}
